---
title: "Function Implementation"
author: "Ixel"
date: "2026-01-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Write a function that computes energy produced from a photovoltaic system if you know the average annual solar radiation. You can use the following formula:

The energy produced by a solar panel system is given by

$$
E = A \cdot r \cdot H \cdot PR
$$
where:

-   $E$ is the energy produced (kWh),
-   $A$ is the solar panel area (m$^2$),
-   $r$ is the panel yield (dimensionless, 0–1), representing manufacturer efficiency (typically $\sim 0.2$),
-   $PR$ is the performance ratio (dimensionless, 0–1), accounting for site-specific losses (typically $\sim 0.75$),
-   $H$ is the annual average solar radiation (kWh m$^{-2}$).

Write your function in R; make sure that you add documentation; include default values for *r* and *PR* in the function definition; save the function in a single file to upload to Canvas.

```{r}
energy_kwh <-
  function(A,r = 0.2,H,PR = 0.75){
    E = A * r * H * PR
    return(E) # store to use later
  }

# test if function works
energy_kwh(A = 8, H = 3)
```


